%provide a detailed description of related papers (not necessarily limited to
%those in the schedule).  If you're proposing a new idea or extending an existing
%approach, compare and contrast it with existing work.  If you're analyzing one
%or two related techniques, describe how they relate to other relevant work;

Scene classification means to provide information about the semantic category or the function of a given image. Among different kidn of scene classification tasks, the indoor scene classification is considered to be one of the most difficult since the lack of discriminative features and contexts at the high level~\cite{Quattoni:2009:RIS}. Spatial pyramid representation\cite{Lazebnik:2006:BBF} is a popular method used for scene classification tasks. It is a simple and computationally efficient extension of an orderless bag-of-features image representation. However, without a proper high-level feature representation, such schemes often fail to offer sufficient semantic information of a scene. Object bank\cite{Li:2010:OBA} is among the first to propose a high-level image representation for scene classification. It uses a large number of pre-trained generic object detectors to create response maps for high level visual recognition tasks. The combination of off-the-shelf object detectors and a simple linear prediction model with a sparse-coding scheme achieves superior predictive power over similar linear prediction models trained on conventional representations. However, this method also limits the performance of their system to the performance of the object detectors they choose. Recently, Convolutional Neural Networks (CNNs) with flexible capacity makes training from large-scale dataset such as ImageNet~\cite{Deng:2009:IAL} possible. In the work of A. Krizhevsky et al.\cite{Krizhevsky:2012:ICD}, they trained one of the largest CNNs on the subsets of ImageNet and achieved better results than any other state-of-the-art methods in 2012. While their CNN system focuses on object detection, the features generated can be used for other applications such as scene classification. Two types of improvements has been done on top of their CNN works. The first type of improvement tries to address the problem of generating possible object locations in an image. Selective search method~\cite{Uijlings:2013:SSO} combines the strength of both an exhaustive search and segmentation and results in a small set of data-driven, class-independent, high quality locations. Girshick et al. propose the Regions with CNN features (R-CNN) method~\cite{Girshick:2013:RFH} as a more effective feature generation method. Alternatively, Zhou et al. try to increase the performance of scene classification using CNN by creating a new scene-centric database~\cite{Zhou:2014:LDF}.